Generate data for NOBA cod ensemble modeling

### 2020-05-27 NOBAcod.Rmd
run truth still breaking at fleets

>>>>

Quick test of `run_truth()` with annage option turned on for NOBA:

```{r testruntruth}

source(here("config/NOBA2Config.R"))

  #Load functional groups
  funct.groups <- atlantisom::load_fgs(dir=d.name,
                           file_fgs = functional.groups.file)
  #Get just the names of active functional groups
  funct.group.names <- funct.groups %>% 
    filter(IsTurnedOn == 1) %>%
    select(Name) %>%
    .$Name

  # # load biolprm file
  #biol <- atlantisom::load_biolprm(d.name, biol.prm.file)
  # 
  # # load run_prm
  # runpar <- atlantisom::load_runprm(d.name, run.prm.file)
  # 
  # # load box info file
  # boxpars <- atlantisom::load_box(d.name, box.file)

testtruth <- atlantisom::run_truth(scenario = scenario.name,
                       dir = d.name,
                       file_fgs = functional.groups.file,
                       file_bgm = box.file,
                       select_groups = funct.group.names,
                       file_init = initial.conditions.file,
                       file_biolprm = biol.prm.file,
                       file_runprm = run.prm.file,
                       file_fish = fisheries.file,
                       verbose = TRUE,
                       annage = TRUE,
                       save = FALSE
    )
